Indoor Dining Shutdowns Negatively Affect Toronto Restaurants’ Performance and Business Practices

### 2021-02-26 outputs/paper/paper.Rmd
Updated title

---
title: "TBD"
subtitle: "TBD"
author: "Najma Osman, Rachit Srivastava, Morgaine Westin, and Bongju Yoo"
thanks: "Code and data are available at: https://github.com/bonjwow/covid-shut-down"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In light of recent COVID-19 restrictions and its impact on businesses, a randomized control trial was conducted by Petit Poll on behalf of the Ontario Government to test the effects of shutting down indoor dining services on restaurants in Toronto. Restaurants who received the intervention and only offered take-out or delivery services experienced a decline in their quarterly revenues compared to the previous quarter and had to make adjustments to the number of employees, menu prices, and operational schedules of their restaurants. Conversely, restaurants in the control group whose indoor dining services remained open during the study period experienced no significant changes in their revenue, employee count, menu prices, or operational schedule compared to the previous corner. While food delivery and take-out services are becoming more popular, these results indicate the value of indoor dining experiences for both restaurants and customers, which the Ontario Government can take into consideration when determining how they can best support Toronto’s growing restaurant industry. "
output:
  bookdown::pdf_document2:
    fig_caption: yes
geometry: margin=0.75in
header-includes:
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \usepackage{longtable}
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Indoor Dining Shutdowns Negatively Affect Toronto Restaurants’ Performance and Business Practices"
author: "Najma Osman, Rachit Srivastava, Morgaine Westin, and Bongju Yoo"
thanks: "Code and data are available at: https://github.com/bonjwow/covid-shut-down"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In light of recent COVID-19 restrictions and its impact on businesses, a randomized control trial was conducted by Petit Poll on behalf of the Ontario Government to test the effects of shutting down indoor dining services on restaurants in Toronto. Restaurants who received the intervention and only offered take-out or delivery services experienced a decline in their quarterly revenues compared to the previous quarter and had to make adjustments to the number of employees, menu prices, and operational schedules of their restaurants. Conversely, restaurants in the control group whose indoor dining services remained open during the study period experienced no significant changes in their revenue, employee count, menu prices, or operational schedule compared to the previous corner. While food delivery and take-out services are becoming more popular, these results indicate the value of indoor dining experiences for both restaurants and customers, which the Ontario Government can take into consideration when determining how they can best support Toronto’s growing restaurant industry. "
output:
  bookdown::pdf_document2:
    fig_caption: yes
geometry: margin=0.75in
header-includes:
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \usepackage{longtable}
toc: FALSE
bibliography: references.bib
---
